### 2020-01-15 Article.tex
Merge

@@

>>>>

During this section we want to study
the asymptotic probability that the 
$r$-neighborhood of a given vertex $v\in \N$
in $G_n$ 
is a tree that belongs to a given $k$-equivalence
class of trees $\mathcal{T}$ with radius at most
$r$. That is, we want to know
\[\Ln \mathrm{Pr}\big( 
T:=N^{G_n}(v;r) \text{ is a tree, and } (T,v)\in \mathcal{T} \big). 
\]
Denote this limit by $\mathrm{Pr}[\mathcal{T}]$. Notice that the definition of  $\mathrm{Pr}[\mathcal{T}]$ does not depend by the
choice of $v$.\\

An easy observation is that if we are given a finite
set of vertices $X \subset \N$ and some

vertex $v\in \N$ and a $k$-equivalence class
of trees $\mathcal{T}$ with radius at most $r$,

@@

%During this section we will consider
%inside of $G_n$ a set of distinguished vertices
%$\overbar{v}\in \N*$ cho
